Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-06-11 performance_comparison.tex
[MGa] some amendments to num res comments

@@

>>>>

The chosen sector was discretized into 140 spatial intervals ($\De s$ = 0.43 m). Both the open- and closed-loop disturbance-aware planning problems were transcribed on this grid in the CasADi-MATLAB environment~\cite{Andersson:MPC:2019}, and the resulting nonlinear programs were solved with IPOPT's interior-point algorithm~\cite{Wachter:MP:2006}.

@@

% Solver times
Solver times (build time is negligible) were measured on a laptop equipped with an Intel Core i9-13980HX with 32 GB RAM.
The reference (nominal) plan, described in Sec.~\ref{sec:nominalFF}, contains 4 200 decision variables and is solved in 7.5 s.
The open-loop robust plan (prediction horizon H = 4) described in Sec.~\ref{sec:open_loop_planning}, expands the model to 48 300 variables, which IPOPT solves in 128 s.
The closed-loop robust plan described in Sec.~\ref{sec:closed_loop_planning} first finds the nominal plan (4 200 vars, 7.5 s), executes a policy-search step (Step 2, Sec.~\ref{sec:LQR}, 20.5 s), and then solves an additional robust problem with 14 700 variables (Step 3, Sec.~\ref{sec:CLrobustified}, 33 s), giving a total of 41 s.
